### 2018-10-28 Sections/economics_of_the_quantum_internet.tex
minor

To formalise this, consider the case where a user purchases an initial single qubit \mbox{$n_\mathrm{user}=1$}, while the global network expands over time as \mbox{$n_\mathrm{global}=N_t$}. Then the classical-equivalent computational power of the user's fixed investment is,

>>>>

To formalise this, consider the case where a user purchases an initial $n$ qubits, while the global network expands over time as $N_t$. Then the classical-equivalent computational power of the user's fixed investment is,
